### 2022-11-17 manuscript.tex
Update response-to-the-reviewers.Rmd [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/366399c3a3d8d06832f71ea5ec300bf690d17bdd.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/366399c3a3d8d06832f71ea5ec300bf690d17bdd/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3490578909

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8d4190ca13a7f11fb128da7e17ec7e4c73eefe31}{SORTEE-Github-Hackathon/manuscript@8d4190c}
on November 17, 2022.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/366399c3a3d8d06832f71ea5ec300bf690d17bdd/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/366399c3a3d8d06832f71ea5ec300bf690d17bdd}{SORTEE-Github-Hackathon/manuscript@366399c}
on November 17, 2022.
